Complementary Filters Shaping\newline Using \(\mathcal{H}_\infty\) Synthesis

### 2019-10-01 presentation/notes.tex
Update presentation for LIGO

% Created 2019-08-28 mer. 16:01
% Intended LaTeX compiler: pdflatex
\documentclass[hangsection=false, titlepage=false, tocnp=false]{cleanreport}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{siunitx}
\newcommand{\authorFirstName}{Thomas}
\newcommand{\authorLastName}{Dehaeze}
\newcommand{\authorEmail}{dehaeze.thomas@gmail.com}
\author{Dehaeze Thomas}
\date{2019-08-28}
\title{Complementary Filters Shaping Using \(\mathcal{H}_\infty\) Synthesis\\\medskip
\large Control System Working Group meeting}
\hypersetup{
 pdfauthor={Dehaeze Thomas},
 pdftitle={Complementary Filters Shaping Using \(\mathcal{H}_\infty\) Synthesis},
 pdfkeywords={complementary filters, h-infinity, sensor fusion},
 pdfsubject={Complementary Filters Shaping Using H-Infinity Synthesis. Presentation during a Control System Working Group Meeting at LIGO.},
 pdfcreator={Emacs 26.2 (Org mode 9.2.5)},
 pdflang={English}}
\begin{document}

@@

\section{Title Slide - Introduction}
\label{sec:org2616a5c}
Hi everyone,

@@

\section{Sensor Fusion Architecture - Noise Filtering}
\label{sec:org3776d94}
A typical sensor fusion architecture is represented here where the signal of two sensors measuring the same quantity \(x\) are filtered out by two filters \(H_1\) and \(H_2\) and then combined to give a estimate \(\hat{x}\) of \(x\).

@@

\section{Sensor Fusion Architecture - Robustness}
\label{sec:org75a0990}
However, in practical systems, the sensor dynamics is never exactly known and cannot be perfectly inverted.

@@

\section{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
\label{sec:org4d70a51}
The design objective is thus to design two complementary filters \(H_1\) and \(H_2\) such that the norms of \(H_1\) and \(H_2\) are below some defined weights \(W_1\) and \(W_2\).

@@

\section{Validation of the proposed synthesis method}
\label{sec:orgd012b55}
We then used this synthesis method to design complementary filters.

@@

\section{Complementary Filters Used at LIGO - Specifications}
\label{sec:orgc32f967}
We then wanted to validate this synthesis method for the design of more complex complementary filters.

@@

\section{\(\mathcal{H}_\infty\) Synthesis - Comparison with LIGO's FIR filters}
\label{sec:orgdb88b2c}
After synthesis, we obtain the complementary filters shown by the dashed curves which are of order 27.
The FIR filters of order 512 develop in the PhD thesis of Hua are also shown by the solid curves.
The filters are quite similar both in phase and in magnitude.

>>>>

% Created 2019-10-01 mar. 09:57
% Intended LaTeX compiler: pdflatex
\documentclass[hangsection=false, titlepage=false, tocnp=false]{cleanreport}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{siunitx}
\newcommand{\authorFirstName}{Thomas}
\newcommand{\authorLastName}{Dehaeze}
\newcommand{\authorEmail}{dehaeze.thomas@gmail.com}
\author{Dehaeze Thomas}
\date{2019-10-01}
\title{Complementary Filters Shaping Using \(\mathcal{H}_\infty\) Synthesis\\\medskip
\large Control System Working Group meeting}
\hypersetup{
 pdfauthor={Dehaeze Thomas},
 pdftitle={Complementary Filters Shaping Using \(\mathcal{H}_\infty\) Synthesis},
 pdfkeywords={complementary filters, h-infinity, sensor fusion},
 pdfsubject={Complementary Filters Shaping Using H-Infinity Synthesis. Presentation during a Control System Working Group Meeting at LIGO.},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

@@

\section{Title Slide - Introduction}
\label{sec:orgda5d0ad}
Hello everyone,

@@

\section{Sensor Fusion Architecture - Noise Filtering}
\label{sec:org498fb95}
A typical sensor fusion architecture is represented here where the signal of two sensors measuring the same quantity \(x\) are filtered out by two filters \(H_1\) and \(H_2\) and then combined to give a estimate \(\hat{x}\) of \(x\).

@@

\section{Sensor Fusion Architecture - Robustness}
\label{sec:org0b2c003}
However, in practical systems, the sensor dynamics is never exactly known and cannot be perfectly inverted.

@@

\section{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
\label{sec:org6d76257}
The design objective is thus to design two complementary filters \(H_1\) and \(H_2\) such that the norms of \(H_1\) and \(H_2\) are below some defined weights \(W_1\) and \(W_2\).

@@

\section{Validation of the proposed synthesis method}
\label{sec:org4885e1d}
We then used this synthesis method to design complementary filters.

@@

\section{Complementary Filters Used at LIGO - Specifications}
\label{sec:org2cb9d01}
We then wanted to validate this synthesis method for the design of more complex complementary filters.

@@

\section{\(\mathcal{H}_\infty\) Synthesis - Comparison with LIGO's FIR filters}
\label{sec:org5ec32cc}
After synthesis, we obtain the complementary filters shown by the dashed curves which are of order 27.
The FIR filters of order 512 develop in the PhD thesis of Hua are also shown by the solid curves.
The filters are quite similar both in phase and in magnitude.

### 2019-10-01 presentation/presentation.tex
Update presentation for LIGO

% Created 2019-08-28 mer. 15:30
% Intended LaTeX compiler: pdflatex
\documentclass[t]{clean-beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{siunitx}
\beamertemplatenavigationsymbolsempty
\addtobeamertemplate{navigation symbols}{}{%
\usebeamerfont{footline}%
\usebeamercolor[fg]{footline}%
\hspace{1em}%
\insertframenumber/\inserttotalframenumber
}
\setbeamertemplate{itemize items}[circle]
\usefonttheme[onlymath]{serif}
\definecolor{mycolor1}{RGB}{79,115,193}
\definecolor{mycolor2}{RGB}{213,91,53}
\usetheme{default}
\author{Dehaeze Thomas}
\date{2019-08-28}
\title{Complementary Filters Shaping\newline Using \(\mathcal{H}_\infty\) Synthesis}
\subtitle{Control System Working Group meeting}
\hypersetup{colorlinks=true}
\hypersetup{
 pdfauthor={Dehaeze Thomas},
 pdftitle={Complementary Filters Shaping\newline Using \(\mathcal{H}_\infty\) Synthesis},
 pdfkeywords={complementary filters, h-infinity, sensor fusion},
 pdfsubject={Complementary Filters Shaping Using H-Infinity Synthesis. Presentation during a Control System Working Group Meeting at LIGO.},
 pdfcreator={Emacs 26.2 (Org mode 9.2.5)},
 pdflang={English}}
\begin{document}

@@

\section{Complementary Filters Shaping}
\label{sec:orgf40a445}
\begin{frame}[label={sec:org644c6eb}]{Sensor Fusion Architecture - Noise Filtering}
\vspace{-1em}
\begin{columns}
\begin{column}{0.45\columnwidth}
\vspace{-1em}
\begin{center}
\includegraphics[scale=1,width=1.1\linewidth]{figs/fusion_super_sensor.pdf}
\end{center}
\end{column}

@@

\begin{frame}[label={sec:orgaee2e4a}]{Sensor Fusion Architecture - Robustness}
\begin{columns}
\begin{column}{0.5\columnwidth}
\vspace{-2em}
\begin{center}
\includegraphics[scale=1,width=1.1\linewidth]{figs/sensor_fusion_dynamic_uncertainty.pdf}
\end{center}
\end{column}

@@

\begin{frame}[label={sec:org1c42552}]{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
\vspace{-1em}
\begin{columns}
\begin{column}{0.5\columnwidth}
\onslide{\begin{cbox}[Design Objective]{blue}{ams nodisplayskip}
\begin{gather*}
  H_1(s) + H_2(s) = 1 \\
  |H_1(j\omega)| \le \frac{1}{|W_1(j\omega)|} \quad \forall\omega \\
  |H_2(j\omega)| \le \frac{1}{|W_2(j\omega)|} \quad \forall\omega
\end{gather*}
\end{cbox}}\vspace{0.5em}

@@

\begin{frame}[label={sec:org493a937}]{Validation of the proposed synthesis method}
\begin{center}
\includegraphics[scale=1,width=0.85\linewidth]{figs/hinf_synthesis_results.pdf}
\end{center}
\end{frame}

\begin{frame}[label={sec:orga95f64f}]{Complementary Filters Used at LIGO - Specifications}
The specification are detailed in \emph{Hua, W., Low frequency vibration isolation and alignment system for advanced LIGO (2005)}

@@

\begin{frame}[label={sec:org3e0dbb2}]{\(\mathcal{H}_\infty\) Synthesis - Comparison with LIGO's FIR filters}
\begin{columns}
\begin{column}{0.6\columnwidth}
\vspace{-3em}
\begin{center}
\includegraphics[scale=1,width=1.1\linewidth]{figs/comp_fir_ligo_hinf.pdf}
\end{center}
\end{column}

>>>>

% Created 2019-10-01 mar. 09:50
% Intended LaTeX compiler: pdflatex
\documentclass[t]{clean-beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{siunitx}
\beamertemplatenavigationsymbolsempty
\addtobeamertemplate{navigation symbols}{}{%
\usebeamerfont{footline}%
\usebeamercolor[fg]{footline}%
\hspace{1em}%
\insertframenumber/\inserttotalframenumber
}
\setbeamertemplate{itemize items}[circle]
\usefonttheme[onlymath]{serif}
\definecolor{mycolor1}{RGB}{79,115,193}
\definecolor{mycolor2}{RGB}{213,91,53}
\usetheme{default}
\author{Dehaeze Thomas \\ Collette Christophe \\ Vermat Mohit}
\date{2019-10-02}
\title{Complementary Filters Shaping\newline Using \(\mathcal{H}_\infty\) Synthesis}
\subtitle{Control System Working Group meeting}
\hypersetup{colorlinks=true}
\hypersetup{
 pdfauthor={Dehaeze Thomas \\ Collette Christophe \\ Vermat Mohit},
 pdftitle={Complementary Filters Shaping\newline Using \(\mathcal{H}_\infty\) Synthesis},
 pdfkeywords={complementary filters, h-infinity, sensor fusion},
 pdfsubject={Complementary Filters Shaping Using H-Infinity Synthesis. Presentation during a Control System Working Group Meeting at LIGO.},
 pdfcreator={Emacs 26.3 (Org mode 9.2.6)},
 pdflang={English}}
\begin{document}

@@

\section{Complementary Filters Shaping}
\label{sec:org15fdac4}
\begin{frame}[label={sec:org236611f}]{Sensor Fusion Architecture - Noise Filtering}
\vspace{-1em}
\begin{columns}
\begin{column}{0.45\columnwidth}
\vspace{-1em}
\begin{center}
\includegraphics[scale=1,width=1.1\linewidth]{figs/fusion_super_sensor.pdf}
\end{center}
\end{column}

@@

\begin{frame}[label={sec:orgb822dd6}]{Sensor Fusion Architecture - Robustness}
\begin{columns}
\begin{column}{0.5\columnwidth}
\vspace{-2em}
\begin{center}
\includegraphics[scale=1,width=1.1\linewidth]{figs/sensor_fusion_dynamic_uncertainty.pdf}
\end{center}
\end{column}

@@

\begin{frame}[label={sec:orge37165c}]{Shaping of Complementary Filters using \(\mathcal{H}_\infty\) synthesis}
\vspace{-1em}
\begin{columns}
\begin{column}{0.5\columnwidth}
\onslide{\begin{cbox}[Design Objective]{blue}{ams nodisplayskip}
\begin{gather*}
  H_1(s) + H_2(s) = 1 \\
  |H_1(j\omega)| \le \frac{1}{|W_1(j\omega)|} \quad \forall\omega \\
  |H_2(j\omega)| \le \frac{1}{|W_2(j\omega)|} \quad \forall\omega
\end{gather*}
\end{cbox}}\vspace{0.5em}

@@

\begin{frame}[label={sec:org1f11fb1}]{Validation of the proposed synthesis method}
\begin{center}
\includegraphics[scale=1,width=0.85\linewidth]{figs/hinf_synthesis_results.pdf}
\end{center}
\end{frame}

\begin{frame}[label={sec:org75dfd29}]{Complementary Filters Used at LIGO - Specifications}
The specification are detailed in \emph{Hua, W., Low frequency vibration isolation and alignment system for advanced LIGO (2005)}

@@

\begin{frame}[label={sec:org53aad0d}]{\(\mathcal{H}_\infty\) Synthesis - Comparison with LIGO's FIR filters}
\begin{columns}
\begin{column}{0.6\columnwidth}
\vspace{-3em}
\begin{center}
\includegraphics[scale=1,width=1\linewidth]{figs/comp_fir_ligo_hinf.pdf}
\end{center}
\end{column}
